On the combination of Set Functions and Failures

### 2016-04-05 docs/src/usage.tex
REPL command ":compile" added

>>>>

\item[\fbox{\code{:compile $prog$}}]\pindex{:compile}
Compile and load the program stored in \code{$prog$.curry},
as with the command \ccode{:load $prog$},
but compile also the generated Haskell modules.
Usually, this is automatically done when an expression is evaluated.
Hence, it is not necessary to use this command.
